Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-07-01 paper/manuscript.tex
Update ABFE cycle figure

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig5_thermo_cyc_abs/Figure_1.pdf}
    \caption{\textbf{Thermodynamic cycle required for an absolute free energy calculation -- absolute free energy of binding example} The fully interacting ligand in water (\textbf{A}), has its charges turned off to pass to (\textbf{B}) followed by turning of van der Waals terms, resulting in a non-interacting ligand in water in (\textbf{C}). Restraints are used on the fully interacting ligand in the binding site of a protein or host molecule (\textbf{D}). The next step is to turn off the charges again (\textbf{E}) followed by the van der Waals interactions resulting in a non-interacting complex state (\textbf{F}). Free energyes can be computed as $\Delta G_{bind} = (\Delta G^{\mathrm{elec}}_{\mathrm{solv}}+ \Delta G^{\mathrm{VdW}}_{\mathrm{solv}})-(\Delta G^{\mathrm{elec}}_{\mathrm{bound}}+ \Delta G^{\mathrm{VdW}}_{\mathrm{bound}}$).
    }
    \label{fig:fig_absolute_thermodynamic_cycle}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig5_thermo_cyc_abs/Figure.png}
    \caption{\textbf{Thermodynamic cycle for an absolute binding free energy calculation with auxiliary restraints} The fully interacting ligand in water (\textbf{A}), has its charges turned off to pass to (\textbf{B}) followed by turning off van der Waals terms, resulting in a non-interacting ligand in water (\textbf{C}). The receptor-ligand complex (\textbf{D}) is defined by binding site restraints (dotted oval). Auxiliary restraints are often introduced (\textbf{E}) to improve convergence while the charges and van der Waals interactions are turned off (\textbf{F} and \textbf{G}). The free energy cost of releasing the auxiliary restraints (\textbf{G} to \textbf{H}) and transferring the non-interacting ligand from the standard state volume to the binding site (\textbf{C} to \textbf{H}) must be accounted for. The standard binding free energy is computed from this cycle as $\Delta G^{\circ}_{\mathrm{bind}} = (\Delta G^{\mathrm{elec}}_{\mathrm{solv}}+ \Delta G^{\mathrm{VdW}}_{\mathrm{solv}}) + \Delta G^{\circ}_{\mathrm{ideal}} -(\Delta G_{\mathrm{aux.restr.}}+\Delta G^{\mathrm{elec}}_{\mathrm{bound}}+ \Delta G^{\mathrm{VdW}}_{\mathrm{bound}}+\Delta G_{\mathrm{release}})$. Many variations of the route between the free (\textbf{A}) and bound (\textbf{D}) states can be used -- for example, state \textbf{H} is commonly skipped and the free energy cost of moving from \textbf{C} to \textbf{G} is calculated directly.}
    \label{fig:fig_absolute_thermodynamic_cycle}
\end{figure}
